Selective electroporation of the viral envelope

### 2021-04-27 documents/pure_electroporation.tex
Spinning off fdtd into submodule

For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control.

@@

First the objective function with an integral power constraint was used, but this did not yield

>>>>

For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.

@@

First the objective function with a constant integral control power constraint was used, but this did not yield
